\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-09-17 paper.tex
Removed some commented out sections

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{showkeys}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifexclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\ifexclude
\notaL{Tal vez esto no lo hicimos:
  \subsection{Morphological studies}
\label{sec:morph-stud}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).} \notaL{¿Sí se midió la porosidad con SEM?}
\fi %exclude

@@

\subsection{PS GRIN Films }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
  \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$G_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to fail close to the border, at distances of the order of the radius
of the cross-section of the o-ring, of the order of a milimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n$ as the distance to the sealing o-ring,
which differed by $0.14\,\text{cm}$ from the corresponding distance
$x_n$ to the wall of the cell.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR}} and \eqref{Eq:Brugg}.
  \label{fig:R20}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \,\text{mA}$
    during a time $t_1=600\,\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\,\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\,\text{cm}$ and
  $x_C=1.7\,\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}

\ifexclude
The thicknesses of the layer were measured
using SEM. In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
$G_1$ taken at the
positions $A$, $B$, and $C$ shown in
Fig. \ref{fig:DR3}. From these micrographs we can
obtain the thicknesses of the porous layer at different
positions. Thus, we obtained that for our sample $G_1$
$d_{1A}= 1320\,\text{nm}$, $ d_{1B} = 997\,\text{nm}$, and $d_{1c} = 605
\,\text{nm}$.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/semD11}
  \caption{Side-view SEM micrographs of the PS GRIN single layer
    taken at positions $A$, $B$, and $C$ of sample $G_1$ shown in
    Fig. \ref{fig:DR3}.
    \notaL{Quité la info redundante}}
  \label{fig:DR4}
\end{figure}
\fi %exclude
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. ****AQUIVOY***

 We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
measured one, though its interference oscillations are larger towards
the blue region probably due to the lack of surface scattering in our
calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
the complex index of refraction corresponding to the fitted porosities.
Similarly, for a second sample $G_2$, etched with a
larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$.

@@

Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
geometry for which the current density may be obtained
analytically. Namely, we can relate the etching rate and the
porosity to the current density by taking measurements at
different positions along just a few PS GRIN samples. Thus, it is much easier
and faster to obtain calibration curves which are useful in the
fabrication of PS photonic structures, GRIN or otherwise.

\notaL{Removí lo de grinMC}
\ifexclude
\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{Cross section SEM images corresponding to the positions
     $A$, $B$, and $C$ of the PS GRIN MC shown in
     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
     different positions, $d_A=2.25\mu\,\text{m}$,
     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
       qué el número de capas no es el mismo en las distintas fotos?
       ¿Por qué no es 6 como dice el texto en la
       Sec. \ref{sec:fabrication-grin-ps}?}
     }
   \label{fig:MCGRIN4}
 \end{figure}
In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
the PS GRIN MC sample. We can appreciate a relatively small interface
roughness and a clear contrast between the high and low porosity
layers. The structure of the microcavity is also visible, with a
central layer of twice the thickness of the corresponding layers
within the Bragg mirrors. The gradient of the thickness is also
evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
of the structure measured at the positions $A$, $B$, and $C$.
The measured thickness are in good agreement with those computed from
the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
  te dio más grande y las otras más chicas? Aquí tienes que decir
  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
\fi %exclude

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{authblk}
%\usepackage[•]{•}ckage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{showkeys}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[normalem]{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newif{\ifinclude}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\newcommand{\notaC}[1]{{\color{green}+C:#1+}}
\newcommand{\notaV}[1]{{\color{red}+V:#1+}}

@@

\ifinclude
\notaL{Tal vez esto no lo hicimos:
  \subsection{Morphological studies}
\label{sec:morph-stud}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).} \notaL{¿Sí se midió la porosidad con SEM?}
\fi %include

@@

\subsection{Samples }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
  \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $G_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the sealing o-ring.}
  \label{fig:SI3}
\end{figure}

In Fig. \ref{fig:SI3} we show a photograph of one of our samples,
$G_3$
prepared as described in Sec. \ref{sec:fabrication-ps-grin}, with the
same conditions as those corresponding to Fig.~\ref{fig:DR1} applying
a current
$I_3=20\,\text{mA}$ during a time $t=250\,s$. We notice a series of
visible interference fringes that get wider as we move towards the
right end of the sample, consistent with a inhomogeneous film that
gets thinner towards the right, and qualitatively consistent with
Fig. \ref{fig:DR1} that shows a current density that decays towards
the right. Equal color lines seem to correspond to iso-current lines of
Fig. \ref{fig:SI3}, except very close to the the walls of the cell,
where the film rapidly becomes very narrow. The reason is that there
is a small region below the cell walls where the electrolyte penetrates
up to the sealing o-ring (see upper panel of
Fig. \ref{fig:DE1}) and towards which the current leaks from the
neighborhood of the wall. The width of this region is
$w=0.14\,\text{cm}$. Thus, we may expect our formula \eqref{Eq:J}
to fail within that region and close to the border, at distances of the order of the radius
of the cross-section of the o-ring, of the order of a milimeter. The
figure shows eight positions
$x'_n=0.2\,\text{cm},0.4\,\text{cm},\ldots,1.6\,\text{cm}$ on which we
measured the near normal incidence reflection spectra of the
sample. Here, we defined $x'_n=x_n+w$ as the distance to the sealing o-ring,
where $x_n$ is the corresponding distance to the wall of the
cell.

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}.
(Table \ref{t:xj}).
\begin{table}
  \centering
  \begin{tabular}{rrr}
    \(x'\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
    from edge& from wall&\\
    \hline
    0.2 & 0.06 & 0.7219\\
    0.4 & 0.26 & 0.6723\\
    0.6 & 0.46 & 0.5769\\
    0.8 & 0.66 & 0.4645\\
    1.0 & 0.86 & 0.3599\\
    1.2 & 1.06 & 0.2749\\
    1.4 & 1.26 & 0.2112\\
    1.6 & 1.46 & 0.1666\\
  \end{tabular}
  \caption{Normalized current density expected at different positions on
    different samples.}
  \label{t:xj}
\end{table}

\subsection{Reflectance}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_3$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R20}
\end{figure}

We measured the reflectance spectra of sample $G_3$ at the positions
indicated in Fig. \ref{fig:SI3}. The results are shown in
Fig. \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$. Notice that the fit is reasonably
good. The contrast of the reflectance in the experiment is smaller
than the fit. We believe this is due to the finite width
\notaL{beams width=?} of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not homogeneous, the
experimental results show an average over regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. This is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths. Similar remarks apply to the fits to the reflectance
spectra of the other samples, incorporated in our supplemental
material (Figs. \ref{fig:R5} and \ref{figR10}).
The results obtained from the reflectance fits are summarized in table
\ref{t:jpdv}.

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
  Sample & current &  density \(j\) & porosity &
  thickness & scale \(s\)& etching rate\\
       & $I$ (mA)      & $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
\hline
$G_1$ & 5  & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
      &    & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
      &    & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
      &    & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
      &    & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
      &    & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
      &    & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
      &    & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
$G_2$ & 10 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
      &    & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
      &    & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
      &    & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
      &    & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
      &    & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
      &    & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
      &    & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
$G_3$ & 20 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
      &    & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
      &    &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
      &    & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
      &    & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
      &    & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
      &    & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
      &    & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
\end{tabular}
\caption{\label{t:jpdv}
  Names of data files, current, current density and fitted parameters:
  porosity, thickness and scale factor.}
\end{table}

\ifinclude
We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
measured one, though its interference oscillations are larger towards
the blue region probably due to the lack of surface scattering in our
calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
the complex index of refraction corresponding to the fitted porosities.
Similarly, for a second sample $G_2$, etched with a
larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$.

@@

Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
geometry for which the current density may be obtained
analytically. Namely, we can relate the etching rate and the
porosity to the current density by taking measurements at
different positions along just a few PS GRIN samples. Thus, it is much easier
and faster to obtain calibration curves which are useful in the
fabrication of PS photonic structures, GRIN or otherwise.
\fi %include
\notaL{Removí lo de grinMC}
\ifinclude
\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

@@

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{Cross section SEM images corresponding to the positions
     $A$, $B$, and $C$ of the PS GRIN MC shown in
     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
     different positions, $d_A=2.25\mu\,\text{m}$,
     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
       qué el número de capas no es el mismo en las distintas fotos?
       ¿Por qué no es 6 como dice el texto en la
       Sec. \ref{sec:fabrication-grin-ps}?}
     }
   \label{fig:MCGRIN4}
 \end{figure}
In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
the PS GRIN MC sample. We can appreciate a relatively small interface
roughness and a clear contrast between the high and low porosity
layers. The structure of the microcavity is also visible, with a
central layer of twice the thickness of the corresponding layers
within the Bragg mirrors. The gradient of the thickness is also
evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
of the structure measured at the positions $A$, $B$, and $C$.
The measured thickness are in good agreement with those computed from
the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
  te dio más grande y las otras más chicas? Aquí tienes que decir
  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
\fi %include

@@

\section{Supplementary material}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_1$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}
